|

### 2022-07-20 Presentations/ISBE2022.Rmd
new plots for the ppt

<!-- \small -->
<!-- One of the replicates of the previous slide, the badge as a handicap -->
```{r, echo=FALSE,fig.align='center', out.width='90%'}
knitr::include_graphics("../Simulations/betCostEvol1_/evolDyn0_betCost5.png")
```

@@

```{r, echo=FALSE,fig.align='center', out.height='90%'}
knitr::include_graphics("../Simulations/betCostEvol1_/evolDyn5_betCost5.png")
```

>>>>

<!-- \small -->
<!-- One of the replicates of the previous slide, the badge as a handicap -->
```{r, echo=FALSE,fig.align='center', out.width='90%'}
# knitr::include_graphics("../Simulations/betCostEvol1_/evolDyn0_betCost5.png")
knitr::include_graphics("../Simulations/betCostEvol2_/evolDyn18_betCost5.png")
```

@@

```{r, echo=FALSE,fig.align='center', out.height='90%'}
knitr::include_graphics("../Simulations/betCostEvol2_/evolDyn19_betCost5.png")
```
